%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Presentations}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}
%---------------------------------------------------------

\cventry
  {Panel presentation of \emph{On the Question of Rural Measurement}} % Role
  {91st Annual Southern Political Science Association Conference} % Event
  {Jan. 2020} % Date(s)
  {San Juan, Puerto Rico} % Location
  {
    \begin{cvitems} % Description(s)
      \item {Presented updates to ongoing original research on the importance of correctly measuring the concepts \emph{rural} and \emph{urban}. Introduced a new measure that vastly outperforms many current approaches.}
    \end{cvitems}
  }

%---------------------------------------------------------
\cventry
  {Panel presentation of \emph{On the Question of Rural Measurement}} % Role
  {47th Annual Florida Political Science Association Conference} % Event
  {Mar. 2019} % Date(s)
  {Tampa, Florida} % Location
  {
    \begin{cvitems} % Description(s)
      \item {Presented original research on the importance of correctly measuring the concepts \emph{rural} and \emph{urban}. Introduced a new measure that vastly outperforms many current approaches.}
    \end{cvitems}
  }

%---------------------------------------------------------
\cventry
  {Poster presentation of \emph{Social Connectedness and Political Behavior in the 2016 U.S. Election}} % Role
  {11th Annual Political Networks Conference and Workshops} % Event
  {Jun. 2018} % Date(s)
  {Arlington, Virginia} % Location
  {
    \begin{cvitems} % Description(s)
      \item {Presented joint research on the relationship between social connectedness, measured in several different ways, and political behaviors and attitudes during the conference's poster session.}
    \end{cvitems}
  }

%---------------------------------------------------------
  \cventry
    {Panel presentation of \emph{Political Trust and Ideological Extremism}} % Role
    {46th Annual Florida Political Science Association Conference} % Event
    {Mar. 2018} % Date(s)
    {Ft. Myers, Florida} % Location
    {
      \begin{cvitems} % Description(s)
        \item {Presented original research on the relationship between political trust and ideological extremism in the United States.}
      \end{cvitems}
    }

%---------------------------------------------------------

\end{cventries}
