%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Research Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
    \cventry
      {Researcher \& Lab Manager} % Job title
      {P.E.B.L. (Politics, Elections, and Behavior Lab)} % Organization
      {Jun. 2018 - Present} % Location
      {} % Date(s)
      {
        \begin{cvitems} % Description(s) of tasks/responsibilities
          \item {Conducted original research, both independently and in collaboration with other lab members, mostly centered on the relationship between place, attitudes, and political behavior in the American context.}
          \item {Directed and supported the original research of junior lab members by maintaining lab resources, assisting with data management and analysis, and providing feedback on manuscripts and other work.}
          \item {Assisted Prof. Jack L Reilly with startup tasks such as the development of standards and guidelines, organization of office space, and the installation of computers and software for the newly founded P.E.B.L. research laboratory.}
      \end{cvitems}
      }


%---------------------------------------------------------
    \cventry
      {Co-author} % Job title
      {Social Connectedness and Political Behavior in the 2016 U.S. Election} % Organization
      {Jan. 2018 - Present} % Location
      {} % Date(s)
      {
        \begin{cvitems} % Description(s) of tasks/responsibilities
          \item {Extended previous work on the relationship between social connectedness and political engagement, and the role of contextual influence, through the use of new measures and fresh data.}
          \item {Performed nearly all data management and statistical analysis, assisted with the production of the manuscript, and authored the appendix.}
          \item {Was awarded a fellowship to support the presentation of a version of the preliminary findings as a poster at the 11th Annual Political Networks Conference and Workshops in Arlington, VA.}
        \end{cvitems}
      }


%---------------------------------------------------------
    \cventry
      {Co-author} % Job title
      {On the Question of Rural Measurement} % Organization
      {Oct. 2018 - Present} % Location
      {} % Date(s)
      {
        \begin{cvitems} % Description(s) of tasks/responsibilities
          \item {Explored the importance of sound measurement specification when modeling relationships between place of residence and political behaviors and attitudes.}
          \item {Used five years of survey data and ten county-level measures of rurality to examine how changing from a continuous to categorical variable influences predictions of behavioral outcomes.}
        \end{cvitems}
      }


%---------------------------------------------------------
    \cventry
      {Author} % Job title
      {Political Trust and Ideological Extremism} % Organization
      {Dec. 2017 - Mar. 2018} % Location
      {} % Date(s)
      {
        \begin{cvitems} % Description(s) of tasks/responsibilities
          \item {Replicated and extended previous quantitative work on the relationship between political trust and ideological extremism.}
          \item {Identified a significant association between conservative ideological extremism and low political trust that had been mischaracterized in previous research due to poor measurement specification and ineffective survey design.}
          \item {Presented findings at a panel session of the 46th Annual Florida Political Science Conference in Ft. Meyers, FL.}
        \end{cvitems}
      }


%---------------------------------------------------------
    \cventry
      {Author} % Job title
      {Politics in Latin America: An Examination of the Cuban Revolution} % Organization
      {Sarasota, Florida} % Location
      {Jan. 2017} % Date(s)
      {
        \begin{cvitems} % Description(s) of tasks/responsibilities
          \item {Reviewed relevant literature on the colonization and historical development of Latin America, and Cuba specifically, to identify factors that made revolution possible.}
          \item {Traced the impact of the revolution through to the modern day, in an attempt to highlight its influence on the Cuban state, U.S.-Cuban relations, and Cuba's role in current regional politics.}
        \end{cvitems}
      }


\end{cventries}
