%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
    \cventry
      {Senior Analyst} % Job title
      {The Analyst Institute} % Organization
      {Sept. 2019 - Present} % Date(s)
      {Washington, D.C.} % Location
      {
        \begin{cvitems} % Description(s) of tasks/responsibilities
          \item {Designed, executed, analyzed, and communicated the results of cutting-edge experimental research on voter mobilization and persuasion.}
          \item {Responsible for simultaneously managing a portfolio of 5 - 10 field experiments at a time, each with a budget between \$100k - \$3M and up to 10 million subjects.}
          \item {Contributed to Analyst Institute's codebase of tools used for data cleaning, statistical analysis, visualization, and reporting.}
      \end{cvitems}
      }


%---------------------------------------------------------
    \cventry
      {Researcher \& Lab Manager} % Job title
      {P.E.B.L. (Politics, Elections, and Behavior Lab)} % Organization
      {Jun. 2018 - Present} % Date(s)
      {Sarasota, Florida} % Location
      {
        \begin{cvitems} % Description(s) of tasks/responsibilities
          \item {Directed and supported the original research of junior lab members by maintaining lab resources, assisting with data management and analysis, and providing feedback on manuscripts and other work.}
          \item {Maintained key infrastructure, such as an up-to-date copy of the Florida Voter File, an open-source geocoder, and additional servers.}
          \item {Assisted with the development of standards and guidelines for research conducted by P.E.B.L.}
      \end{cvitems}
      }

%---------------------------------------------------------
    \cventry
      {Teaching Assistant} % Job title
      {Department of Political Science, New College of Florida} % Organization
      {Aug. 2017 - May 2019} % Date(s)
      {Sarasota, Florida} % Location
      {
        \begin{cvitems} % Description(s) of tasks/responsibilities
          \item {Planned and coordinated multiple exercises, workshops, and in class discussions on topics covered in American government and quantitative social science methods courses.}
          \item {Taught multiple sessions on the fundamentals of debate, including writing cases, preparing and engaging in cross examination, and delivering rejoinders and rebuttals.}
        \end{cvitems}
      }

%---------------------------------------------------------
  \cventry
    {Pretrial Services Intern} % Job title
    {12th Judicial Circuit Court} % Organization
    {Jun. 2018 - Aug. 2018} % Date(s)
    {Sarasota, Florida} % Location
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Interviewed each newly arrested person and compiled relevant case history into a comprehensive report for judges presiding over First Appearance, as well as the Office of the Public Defender and the Office of the State Attorney.}
        \item {Reviewed each new inmate’s file to determine eligibility for special court programs, such as mental health court, drug court, and DUI court.}
        \item {Interviewed victims of violent and domestic crimes to verify information and gather victim statements for the court.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Student Law Clerk} % Job title
    {Office of the General Counsel, New College of Florida} % Organization
    {Jan. 2018 - May 2018} % Date(s)
    {Sarasota, Florida} % Location
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Evaluated the effectiveness and suitability of the then-current Title IX policy and worked with internal departments and external advisors to develop and propose revisions.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Lead Station Cook \& Certified Designated Trainer} % Job title
    {The Cheesecake Factory, Inc.} % Organization
    {Jul. 2015 - Mar. 2018} % Date(s)
    {Ft. Lauderdale \& Sarasota, Florida} % Location
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Prepared station for shift, cooked all orders quickly and according to recipe, cleaned and organized station after shift, and assisted other members of the kitchen team.}
        \item {Trained new cooks on the Pasta and Sauté stations, the two highest volume and most demanding stations in the kitchen.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Legal Intern} % Job title
    {Legal Aid of Manasota, Inc.} % Organization
    {Jan. 2017 - Dec. 2017} % Date(s)
    {Sarasota, Florida} % Location
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Supported staff attorneys by drafting complaints, motions, and answers as requested.}
        \item {Accompanied staff attorneys in their appearances before the 12th Circuit Court.}
        \item {Assisted with client intake and review of client provided documents such as leases, contracts, correspondence, and notices.}
        \item {Contributed to weekly case review by researching and presenting applicable statutes, codes, regulations, and case law.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Campaign Manager} % Job title
    {Fredd Atkins for Sarasota County Commissioner} % Organization
    {Apr. 2016 - Nov. 2016} % Date(s)
    {Sarasota, Florida} % Location
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Effectively managed all aspects of the county-wide campaign, including fundraising, messaging, scheduling, recruitment, budgeting, and voter outreach.}
        \item {Developed and implemented a fundraising plan that raised nearly \$100,000 from individual donors and local interest groups.}
        \item {Led the implementation of a digital outreach campaign that returned an above average engagement and click through rate.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Organizing Fellow} % Job title
    {Charlie Crist for Governor} % Organization
    {Aug. 2014 - Nov. 2014} % Date(s)
    {Coral Springs, Florida} % Location
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Recruited, trained, and coordinated volunteers.}
        \item {Scheduled staff and managed phone banks at the Coral Springs, Florida office.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
